Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-10 second-draft/pnas-word-order-si.tex
SI

\begin{figure} 
	\begin{center}
	\includegraphics[width=0.32\textwidth]{../results/correlations/figures/pred-eff-families-2.pdf}
	\end{center}
	\caption{Order of the eight correlates across 51 languages, in the real grammars (left) and predicted by efficiency optimization (right). Dark blue: Verb patterner \emph{precedes} object patterner(English, Arabic, ...). Light blue: Verb patterner \emph{follows} object patterner (Japanese, Hindi , ...) \textcolor{red}{add other functions to this plot}.}\label{fig:per-lang}
\end{figure}

@@

\begin{figure}
    \centering

    \includegraphics[scale=.25]{../results/correlations/figures/coverage-langmod-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/figures/coverage-parse-best.pdf}
    \includegraphics[scale=.25]{../results/correlations/figures/coverage-two-lambda09-best.pdf}

    \includegraphics[scale=.25]{../results/correlations/figures/coverage-ground.pdf}
    \includegraphics[scale=.25]{../results/correlations/figures/coverage-depl.pdf}
	\caption{Correlations satisfied by the best word order grammars for predictability, parseability, efficiency, by the UD languages, and by the best grammars for dependency length.}
    \label{fig:posterior-prevalence}
\end{figure}

@@

For each of the six syntactic relation, the first column provides the ordered coded in the extracted grammar; the second column provides the order coded in WALS (DH for dependent-head, HD for head-dependent order). `?' indicates that WALS has no data.
$*$ indicates that WALS does not list a dominant order, which can mean that both orders occur in the language, or that insufficient data was available when compiling WALS \citep{dryer2011evidence}.
Finally, `--' indicates that the relation does not occur in the corpus.

>>>>

We show results on the level of individual languages in Figure~\ref{fig:per-lang}.

\begin{figure} 
	\begin{center}
	\includegraphics[width=0.7\textwidth]{../results/correlations/figures/pred-eff-pred-pars-families-2.pdf} % figures/pred-eff-families-2.pdf
	\end{center}
	\caption{Order of the eight correlates across 51 languages, in the real grammars (left) and predicted by optimizing for efficiency, predictability, parseability (right). Dark blue: Verb patterner \emph{precedes} object patterner (English, Arabic, ...). Light blue: Verb patterner \emph{follows} object patterner (Japanese, Hindi , ...). White cells indicate that the relation is not annotated in the dataset for the given language. \textcolor{red}{say more about how these predictions were generated}}\label{fig:per-lang}
%	\caption{Order of the eight correlates across 51 languages, in the real grammars (left) and predicted by efficiency optimization (right). Dark blue: Verb patterner \emph{precedes} object patterner(English, Arabic, ...). Light blue: Verb patterner \emph{follows} object patterner (Japanese, Hindi , ...) \textcolor{red}{add other functions to this plot}.}\label{fig:per-lang}
\end{figure}

@@

%\begin{figure}
%    \centering
%    
%    \includegraphics[scale=.25]{../results/correlations/figures/coverage-langmod-best.pdf}
%    \includegraphics[scale=.25]{../results/correlations/figures/coverage-parse-best.pdf}
%    \includegraphics[scale=.25]{../results/correlations/figures/coverage-two-lambda09-best.pdf}
%    
%    
%    \includegraphics[scale=.25]{../results/correlations/figures/coverage-ground.pdf}
%    \includegraphics[scale=.25]{../results/correlations/figures/coverage-depl.pdf}
%	\caption{Correlations satisfied by the best word order grammars for predictability, parseability, efficiency, by the UD languages, and by the best grammars for dependency length.}
%    \label{fig:posterior-prevalence}
%\end{figure}

@@

For each of the six syntactic relation, the first column provides the ordered coded in the extracted grammar; the second column provides the order coded in WALS (DH for dependent-head, HD for head-dependent order). `?' indicates that WALS has no data.
$*$ indicates that WALS does not list a dominant order, which can mean that both orders occur at similar rates in the language, or that insufficient data was available when compiling WALS \citep{dryer2011evidence}.
Finally, `--' indicates that the relation does not occur in the corpus.
